Renewal and stability in populations structured by remaining years of life

### 2015-10-15 ThanoRepro/ThanoRepro.tex
changes taken. Ugly conflicts because I forgot to fold in PC changes. Now merged finally. Sucks you can't overwrite remote when using merge tool...
change affil
added funding disclaimer, since work was mostly done in Berkeley

\documentclass{article}
\usepackage{appendix}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{placeins}
\usepackage{graphicx}
\usepackage{subcaption}
%\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows}
%\usepackage[active,tightpage]{preview}
%\PreviewEnvironment{tikzpicture}
%\setlength\PreviewBorder{5pt}
\usepackage{natbib}
\bibpunct{(}{)}{,}{a}{}{;} 
\usepackage{url}
\usepackage{nth}
% for the d in integrals
\newcommand{\dd}{\; \mathrm{d}}
\newcommand{\ec}{\quad\quad\text{,}}
\newcommand{\ep}{\quad\quad\text{.}}

\usepackage[top=2in, bottom=1.5in, left=1in, right=1in]{geometry}
\usepackage{setspace}
% matrix numbering
\usepackage{trivfloat}
\trivfloat{matrix}
\floatstyle{plaintop}
    \restylefloat{matrix}
\AtBeginDocument{\numberwithin{matrix}{section}}

@@

\title{Renewal and stability in populations structured by remaining
years of life}
\author{Tim Riffe \\ University of California, Berkeley}
\maketitle

\begin{abstract}
A unisex model of population renewal for populations structured by
thanatological age is presented in both continuous and discrete form. Various
stable and transient properties populations are compared and related when viewed
by chronological versus thanatological age. Results from the two age perspectives are conformable if the starting
population is stable, but are otherwise divergent.
\end{abstract}

>>>>

\documentclass{article}
\usepackage{appendix}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{placeins}
\usepackage{graphicx}
\usepackage{subcaption}
%\usepackage{pgf}
\usepackage{tikz}
%\usetikzlibrary{arrows}
%\usepackage[active,tightpage]{preview}
%\PreviewEnvironment{tikzpicture}
%\setlength\PreviewBorder{5pt}
\usepackage{natbib}
\bibpunct{(}{)}{,}{a}{}{;} 
\usepackage{url}
\usepackage{nth}
% for the d in integrals
\newcommand{\dd}{\; \mathrm{d}}
\newcommand{\ec}{\quad\quad\text{,}}
\newcommand{\ep}{\quad\quad\text{.}}

\usepackage[top=2in, bottom=1.5in, left=1in, right=1in]{geometry}
\usepackage{setspace}
\newcommand\ackn[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

% matrix numbering
\usepackage{trivfloat}
\trivfloat{matrix}
\floatstyle{plaintop}
    \restylefloat{matrix}
\AtBeginDocument{\numberwithin{matrix}{section}}

@@

\title{Renewal and stability in populations structured by remaining
years of life}
\author{Tim Riffe \\ Max Planck Institute for Demographic Research}
\maketitle

\begin{abstract}
A unisex model of population renewal for populations structured by
thanatological age is presented in both continuous and discrete form. Various
stable and transient properties populations are compared and related when viewed
by chronological versus thanatological age. Results from the two age perspectives are conformable if the starting
population is stable, but are otherwise divergent.\ackn{Research reported in this manuscript
was supported by the U.S.
National Institute On Aging of the National Institutes of Health under award numbers R01-AG011552 and R01-AG040245 and by the Spanish Ministry of Science and Innovation under award
number ECO2013-48326-C2-1-P. The content is solely the responsibility of the
author and does not necessarily represent the official views of the funding
agencies.}
\end{abstract}
